Exploratory data structure comparisons: Three new tools based on Principal Component Analysis

### 2017-03-23 article/article_v0.9.tex
Edited section about PCADSC tools (now section 2)

\subsubsection{The chroma plot}
This plot compares the loadings of the two datasets. The chroma plot consists of two panels, one for each dataset, made up of colored bars. These bars each represent a principal component and their coloring illustrates the relative weights of the $d$ original variables, that is, their absolute, normalized loading contributions. More specifically, when illustrating the $i$th principal component, we plot a vertical bar of length one that has been divided into $d$ segments of different colors and the wideness of the $j$th such segment is given by 
$$\omega_{ij} = \frac{|(\eta_i)_j|}{\sum_{k=1}^d |(\eta_i)_k|}$$
where $(\eta_i)_j$ denotes the $j$th entry of $\eta_i$. Due to the indeterminacy of the sign, all the signs are removed from the coefficients in the loadings. The bars are ordered according to the variation components and they are annotated with the cumulative percentage explained variance of that component, that is, the scaled and summed variance component contributions,
$$\tilde\sigma^c_i = \frac{\sum_{j = 1}^i \lambda_i}{\sum_{k=1}^d \lambda_k} = \frac{\sum_{j = 1}^i \lambda_i}{d}$$
Especially when $d$ is large, we recommend plotting only a select set of interesting principal components, e.g. as identified by use of the angle plot. In this scenario, the annotations should rather be the non-cumulative variance contributions, $\tilde\sigma_i = \frac{\lambda_i}{d}$.

>>>>

\subsubsection{The chroma plot}
This plot compares the loadings of the two datasets. The chroma plot consists of two panels, one for each dataset, made up of colored bars. These bars each represent a principal component and their coloring illustrates the relative weights of the $d$ original variables, that is, their absolute, normalized loading contributions. More specifically, when illustrating the $i$th principal component, we plot a vertical bar of length one that has been divided into $d$ segments of different colors and the wideness of the $j$th such segment is given by 
$$\omega_{ij} = \frac{|(\eta_i)_j|}{\sum_{k=1}^d |(\eta_i)_k|}$$
where $(\eta_i)_j$ denotes the $j$th entry of $\eta_i$. Due to the indeterminacy of the sign, all the signs are removed from the coefficients in the loadings. The bars are ordered according to the variation components and they are annotated with the cumulative percentage explained variance of that component, that is, the scaled and summed variance component contributions,
$$\sigma_c = \frac{\sum_{j = 1}^i \lambda_i}{\sum_{k=1}^d \lambda_k} = \frac{\sum_{j = 1}^i \lambda_i}{d}$$
Especially when $d$ is large, we recommend plotting only a select set of interesting principal components, e.g. as identified by use of the angle plot. In this scenario, the annotations should rather be the non-cumulative variance contributions, $\frac{\lambda_i}{d}$.
